### 2016-10-01 results.tex
pus

\begin{proof}
The proof follows the same high-level ideas as in the proof of
Theorem~\ref{fig:DS-bigram}, based on the observation that ${\sf
leak}_\cap(S)$ suffices to determine the overlap in calls to the
pseudorandom function~$F$.

@@

The proof that this provides a good simulation is identical to that
of Theorem~\ref{fig:DS-bigram}. \hfill\qed
\end{proof}

>>>>

\begin{proof}
The proof follows the same high-level ideas as in the proof of
Theorem~\ref{thm:priv-ss}, based on the observation that ${\sf
leak}_\cap(S)$ suffices to determine the overlap in calls to the
pseudorandom function~$F$.

@@

The proof that this provides a good simulation is identical to that
of Theorem~\ref{thm:priv-ss}. \hfill\qed
\end{proof}
